A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-16 doc/sigchi14/targeting.tex
add time-vs-list-order figure to the text

\subsection{Measures}
The main measures were {\bf target acquisition time}: the time required to identify, select, and connect to a wireless target device; and{\bf user preference}: which interface users preferred for the task after completing the study.

@@

>>>>

\subsection{Measures}
The main measures were {\bf target acquisition time}: the time required to identify, select, and connect to a wireless target device; and {\bf user preference}: which interface users preferred for the task after completing the study.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/R_List_by_Target.pdf}
\caption{Average time taken vs. the order of nodes on the list }
\label{fig:time-vs-list-order}
\end{figure}
